\documentclass[11pt]{article}

\input{Shared.tex}

\parindent0in
\pagestyle{plain}
\thispagestyle{plain}

\usepackage{csquotes}
\usepackage[shortlabels]{enumitem}

\newcommand{\dated}{\today}
\newcommand{\token}[1]{\langle \text{#1} \rangle}

\begin{document}

\textbf{Introduction to the Theory of
Computation}\hfill\textbf{\myname}\\[0.01in]
\textbf{Chapter 5: Reducibility}\hfill\textbf{\dated}\\
\smallskip\hrule\bigskip

\begin{problem}{5.14}
Consider the problem of determining whether a Turing machine $M$ on an input
$w$ ever attempts to move its head left when its head is on the left-most tape cell. Formulate this problem as a language and show that it is undecidable.
\end{problem}

\begin{proof}
Let $T = \{\langle M, w \rangle \ | \ M \text{ is a \textbf{TM}, which on input } w \text{ moves its head left when its head is on the} \\ \text{left-most tape cell}\}$. \\

Show that $A_{TM}$ reduces to $T$, where $A_{TM} = \{\langle M, w \rangle \ | \ M \text{ is a \textbf{TM} and } M \text{ accepts } w\}$. Assume for the sake of contradiction that \textbf{TM} $R$ decides $T$. Then construct a \textbf{TM} $S$ that uses $R$ to decide $A_{TM}$. The idea is to construct a new \textbf{TM} $M_w$, which only moves its head left when its head is on the left-most tape cell if $M$ accepts $w$. We construct \textbf{TM} $M_w$ using 2 tapes as follows. \\

$M_w =$ \textquotedblleft On input $w$:
\begin{enumerate}
\item Simulate $M$ on $w$ using the second tape.
\item If the simulation shows that $M$ accepts, move the head of the first tape left.\textquotedblright
\end{enumerate}

Next, we construct \textbf{TM} $S$ to decide $A_{TM}$. \\

$S =$ \textquotedblleft On input $\langle M, w \rangle$, where $M$ is a \textbf{TM} and $w$ is a string:
\begin{enumerate}
\item Use $M$ and $w$ to construct \textbf{TM} $M_w$ as discussed above.
\item Convert the 2 tape \textbf{TM} $M_w$ to equivalent single tape \textbf{TM} $M'$.
\item Run $R$ on $\langle M', w \rangle$.
\item If $R$ accepts, $M$ accepts $w$, so \textit{accept}. Otherwise, \textit{reject}.\textquotedblright
\end{enumerate}
Thus, if \textbf{TM} $R$ exists, we can decide $A_{TM}$, but we know that $A_{TM}$ is undecidable\footnote{Theorem 4.11 $A_{TM}$ is undecidable.}. By virtue of this contradiction, we can conclude that $R$ does not exist. Therefore, $T$ is undecidable.
\end{proof}
\end{document}