\documentclass[11pt]{article}

\input{Shared.tex}

\parindent0in
\pagestyle{plain}
\thispagestyle{plain}


\usepackage{csquotes}

\newcommand{\dated}{\today}
\newcommand{\token}[1]{\langle \text{#1} \rangle}

\begin{document}

\textbf{Introduction to the Theory of
Computation}\hfill\textbf{\myname}\\[0.01in]
\textbf{Chapter 3: The Church-Turing Thesis}\hfill\textbf{\dated}\\
\smallskip\hrule\bigskip

\begin{problem}{3.18}
Show that a language is decidable iff some enumerator enumerates the language in the standard string order.
\end{problem}

The proof is in two parts.

\begin{problem}[Part]{a}
If a language is decidable, then some enumerator enumerates the language in
the standard string order.
\end{problem}

\begin{proof}
For any decidable language $L$, let $M$ be the \textbf{TM}s that decides it. We construct an enumerator $E$ that enumerates $L$ in the standard string order: \\
\\
$E = $ \textquotedblleft Ignore the input:
\begin{enumerate}
\item Repeat the following for $i = 1,2,3, \cdots$
\item \hspace*{0.5cm} Generate all possible strings $s_1,s_2,s_3,\cdots$ of length $i$, where each $s_k \in \Sigma^{*}$.
\item \hspace*{0.5cm} Sort the strings in standard string order.
\item \hspace*{0.5cm} Run $M$ on each $s_k$. If $M$ accepts $s_k$, \textit{print} $s_k$.\textquotedblright
\end{enumerate}

\end{proof}

\begin{problem}[Part]{b}
If some enumerator enumerates a language in the standard string order, then the language is decidable.
\end{problem}

\begin{proof}
For any Turing-recognizable language $L$, let $E$ be the enumerator that enumerates it in the standard string order. We construct a \textbf{TM} $M$ that decides it:\\
\\
\textquotedblleft On input string $w$:
\begin{enumerate}
\item Run the enumerator $E$.
\item Repeat the following for each string $s$ printed by $E$.
\item \hspace*{0.5cm} If $w = s$, \textit{accept}.
\item \hspace*{0.5cm} If $w$ precedes $s$ in the standard string order, then continue. Otherwise \textit{reject}.
\item If $E$ halts, \textit{reject}.\textquotedblright
\end{enumerate}
\end{proof}

\end{document}