\documentclass[11pt]{article}

\input{Shared.tex}

\parindent0in
\pagestyle{plain}
\thispagestyle{plain}

\usepackage{csquotes}
\usepackage[shortlabels]{enumitem}

\newcommand{\dated}{\today}
\newcommand{\token}[1]{\langle \text{#1} \rangle}

\begin{document}

\textbf{Introduction to the Theory of
Computation}\hfill\textbf{\myname}\\[0.01in]
\textbf{Chapter 8: Space Complexity}\hfill\textbf{\dated}\\
\smallskip\hrule\bigskip

\begin{problem}{8.27}
Recall that a directed graph is strongly connected if every two nodes are connected by a directed path in each direction. Let
\[
STRONGLY\text{-}CONNECTED = \{\langle G \rangle \ | \ G \text{ is a strongly connected graph}\}.
\]
Show that $STRONGLY\text{-}CONNECTED$ is NL-complete.
\end{problem}

\begin{proof}
To show that $STRONGLY\text{-}CONNECTED$ is NL-complete, we must show that it is in NL and that all NL problems are log space reducible to it. To show $STRONGLY\text{-}CONNECTED \in$ NL, we give an algorithm $S$ that decides $\overline{STRONGLY\text{-}CONNECTED}$ in non-deterministic log space. \\

$S =$ \textquotedblleft On input $\langle G \rangle$, where $G$ is a directed graph:
\begin{enumerate}
\item Non-deterministically select every distinct pair of nodes $s$ and $t$ in $G$:
\item \hspace*{0.5cm} Run the algorithm $M$ for $\overline{PATH}$ given in Theorem 8.27 on $\langle G, s, t \rangle$.
\item \hspace*{0.5cm} \textit{Accept}, if $M$ accepts. \textit{Reject}, if $M$ rejects.\textquotedblright
\end{enumerate}

To prove that $STRONGLY\text{-}CONNECTED$ is NL-hard, we give a log space reduction from $PATH$ to $STRONGLY\text{-}CONNECTED$. This reduction converts a directed graph $G$ and two nodes $s$ and $t$ to a directed graph $G'$ so that $G$ has directed path from $s$ to $t$, iff $G'$ is strongly connected. Next, we show how to construct the graph $G'$. The graph $G'$ is same as the graph $G$, but includes following additional edges, which we name connectivity edges:
\begin{enumerate}
\item An edge to $s$ from every node in $G$ except $t$.
\item An edge from $t$ to every node in $G$ except $s$.
\end{enumerate}

Suppose graph $G$ contains a path from node $s$ to $t$. Then, $G'$ is strongly connected, because a path from any two distinct nodes $u$ and $v$ in $G'$ can be constructed as follows:
\begin{enumerate}
\item Start at node $u$, and go to $s$.
\item Follow the path from $s$ to $t$.
\item Go to node $v$.
\end{enumerate}

Suppose $G'$ is strongly connected. Then, there are two distinct nodes $s$ and $t$ in $G'$, such that there is an edge to $s$ from every other node in $G'$ except $t$, and there is an edge from $t$ to every other node in $G'$ except $s$. $G'$ also contains a path from node $s$ to $t$, and removing connectivity edges from $G'$ to construct $G$ does not remove this path from $s$ to $t$ in $G$. A log space transducer can easily implement construction of $G'$ from $G$, $s$ and $t$. Hence, $STRONGLY\text{-}CONNECTED$ is NL-hard.
\end{proof}
\end{document}