\documentclass[11pt]{article}

\input{Shared.tex}

\parindent0in
\pagestyle{plain}
\thispagestyle{plain}

\newcommand{\dated}{\today}

\begin{document}

\textbf{Introduction to the Theory of
Computation}\hfill\textbf{\myname}\\[0.01in]
\textbf{Chapter 2: Context-Free Languages}\hfill\textbf{\dated}\\
\smallskip\hrule\bigskip

\begin{problem}{2.36}
Give an example of a language that is not context free but that acts like a CFL in the pumping lemma. Prove that your example works.
\end{problem}

\begin{idea}[Informal description.]
The language $A = \{a^nb^nc^n \ | \ n \geq 0 \}$ is easily seen to be a non-CFL. So is $B = \{a^ib^jc^jd^k \ | \ i,j,k \geq 0, \ if \ i = 1 \ then \ k = j \}$. We show that the language $B$ acts like a CFL in the pumping lemma.
\end{idea}

\begin{proof}
Assume the language $B = \{a^ib^jc^jd^k \ | \ i,j,k \geq 0, \ if \ i = 1 \ then \ k = j \}$ is context free. Let $p$ be the pumping length given by the pumping lemma. The pumping length $p$ is at least 2, because the strings $a$ and $b$ cannot be divided and pumped. The strings $ab$, $cc$ and $dd$ can be divided and pumped according to the method given below.
\\
\\
Choose $s$ to be any string, such that $s \in B$ and $|s| \geq p$. The pumping lemma states that $s$ can be pumped. There are three cases:

\begin{enumerate}
\item $i = 0$. In other words, a's are missing. There are two sub-cases:
\begin{enumerate}
\item $j = 0$. This means that the string $s$ contains only d's. Let $u = \varepsilon$, $v$ be the first d, $x = \varepsilon$, $y = \varepsilon$, and $z$ is the rest.
\item $j > 0$. Let $u = \varepsilon$, $v$ be the last b, $x = \varepsilon$, $y$ be the first c,  and $z$ is the rest.
\end{enumerate}
\item $i = 1$. In this case the string $s$ contains equal number of b's, c's and d's. Let $u = \varepsilon$, $v = a$, $x = \varepsilon$, $y = \varepsilon$, and $z$ is the rest.
\item $i > 1$. There are three sub-cases:
\begin{enumerate}
\item $j = 0$, and $k = 0$. The string $s$ only contains a's. Let $u = \varepsilon$, $v$ be the first a, $x = \varepsilon$, $y = \varepsilon$, and $z$ is the rest.
\item $j = 0$, and $k > 0$. Let $u = \varepsilon$, $v$ be the first d, $x = \varepsilon$, $y = \varepsilon$, and $z$ is the rest.
\item $j > 0$. Let $u = \varepsilon$, $v$ be the last b, $x = \varepsilon$, $y$ be the first c,  and $z$ is the rest.
\end{enumerate}
\end{enumerate}

This method of dividing the string $s$ works no matter what $s$ is, and all three conditions of the pumping lemma are satisfied:
\begin{enumerate}
\item $uv^ixy^iz \in B, \ for \ each \ i \geq 0$
\item $|vy| > 0$
\item $|vxy| \leq p$
\end{enumerate}

Therefore, even though the language $B$ is not a CFL, but it acts like a CFL in the pumping lemma.
\end{proof}

\end{document}
