\documentclass[11pt]{article}

\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{fancyvrb}

\parindent0in
\pagestyle{plain}
\thispagestyle{plain}

\newcommand{\myname}{Mehshan Mustafa}
\newcommand{\dated}{\today}

\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{problem}[2][Problem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{question}[2][Question]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{solution}{\begin{proof}[Solution]}{\end{proof}}
\newenvironment{idea}[2][Proof Idea.]{\textit{#1} #2}

\begin{document}

\textbf{Introduction to the Theory of
Computation}\hfill\textbf{\myname}\\[0.01in]
\textbf{Chapter 1: Regular Languages}\hfill\textbf{\dated}\\
\smallskip\hrule\bigskip

\begin{problem}{1.55}
The pumping lemma says that every regular language has a pumping length $p$, such that every string in the language can be pumped if it has length $p$ or more. If $p$ is a pumping length for language $A$, so is any length $p' \geq p$. The minimum pumping length for $A$ is the smallest $p$ that is a pumping length for $A$. For example, if $A = 01^{*}$, the minimum pumping length is 2. The reason is that the string $s = 0$ is in $A$ and has length 1 yet $s$ cannot be pumped; but any string in $A$ of length 2 or more contains a 1 and hence can be pumped by dividing it so that $x = 0$, $y = 1$, and $z$ is the rest. For each of the following languages, give the minimum pumping length and justify your answer.
\end{problem}

\begin{problem}[Part]{a}
$0001^{*}$
\end{problem}
The minimum pumping length is 4. The strings 0, 00 and 000 cannot be divided and pumped. The string $s=0001$ can be pumped by dividing it so that $x=000$, $y=1$, and $z$ is the rest.

\begin{problem}[Part]{d}
$0^{*}1^{+}0^{+}1^{*} \cup 10^{*}1$
\end{problem}
The minimum pumping length for $0^{*}1^{+}0^{+}1^{*}$ is 2, because all strings in it are at least of length 2, contain at least one 1 and 0, and can be pumped by dividing according to following two cases.
\begin{enumerate}
\item If the string $s$ starts with 0, then it can be pumped by dividing it so that $x=\epsilon$, $y=0$, and $z$ is the rest.
\item If the string $s$ starts with 1, then it can be pumped by dividing it so that $x=\epsilon$, $y=1$, and $z$ is the rest.
\end{enumerate}

The minimum pumping length for $10^{*}1$ is 3. The strings 1 and 11 can not be pumped. A string of length at least 3 contains at least one 0, so it can be pumped by dividing it so that $x=1$, $y=0$, and $z$ is the rest.
\\
\\
The minimum pumping length for $0^{*}1^{+}0^{+}1^{*} \cup 10^{*}1$ is 3, because 11 cannot be pumped.

\end{document}