\documentclass[11pt]{article}

\input{Shared.tex}

\parindent0in
\pagestyle{plain}
\thispagestyle{plain}

\usepackage{csquotes}
\usepackage[shortlabels]{enumitem}

\newcommand{\dated}{\today}
\newcommand{\token}[1]{\langle \text{#1} \rangle}

\begin{document}

\textbf{Introduction to the Theory of
Computation}\hfill\textbf{\myname}\\[0.01in]
\textbf{Chapter 8: Space Complexity}\hfill\textbf{\dated}\\
\smallskip\hrule\bigskip

\begin{problem}{8.16}
The game of \textbf{\textit{Nim}} is played with a collection of piles of sticks. In one move, a player may remove any nonzero number of sticks from a single pile. The players alternately take turns making moves. The player who removes the very last stick loses. Say that we have a game position in Nim with $k$ piles containing $s_1, \ldots ,s_k$ sticks. Call the position \textbf{\textit{balanced}} if each column of bits contains an even number of 1s when each of the numbers $s_i$ is written in binary, and the binary numbers are written as rows of a matrix aligned at the low order bits. Prove the following two facts.
\end{problem}

\begin{problem}[Part]{a}
Starting in an unbalanced position, a single move exists that changes the position into a balanced one.
\end{problem}

\begin{proof}
Starting in an unbalanced position, we give steps to find a single move that changes the position into a balanced one.
\begin{enumerate}
\item Find the left most column $k$ with odd number of 1s. In an unbalanced position at least one $s_i$ will have a 1 in column $k$. Pick one such $s_i$.
\item Go from column $k$ to column 1 in selected $s_i$ and change 1 to 0 or 0 to 1 to get a balance position.
\item Subtract the new number produced in previous step from original $s_i$. The result is the number of sticks that can be removed from pile $s_i$ to get a balance position.
\end{enumerate}
\end{proof}

\begin{problem}[Part]{b}
Starting in a balanced position, every single move changes the position into an unbalanced one.
\end{problem}

\begin{proof}
Starting in a balanced position, and removing some non-zero number of sticks from a pile changes the number of sticks in the pile. This new number has a different combination of 1s and 0s. So some column will loose even number of 1s.
\end{proof}

\begin{problem}[Part]{c}
Let $NIM = \{\langle s_1, \ldots , s_k \rangle \ | \ \text{each } s_i \text{ is a binary number and Player I has a winning
strategy} \\ \text{in the Nim game starting at this position}\}$. Use the preceding facts about balanced positions to show that $NIM \in$ L.
\end{problem}

\begin{proof}
\end{proof}

\end{document}