\documentclass[11pt]{article}

\input{Shared.tex}

\parindent0in
\pagestyle{plain}
\thispagestyle{plain}

\newcommand{\dated}{\today}

\begin{document}

\textbf{Introduction to the Theory of
Computation}\hfill\textbf{\myname}\\[0.01in]
\textbf{Chapter 2: Context-Free Languages}\hfill\textbf{\dated}\\
\smallskip\hrule\bigskip

\begin{problem}{2.31}
Let $B$ be the language of all palindromes over ${0,1}$ containing equal numbers of 0s and 1s. Show that $B$ is not context free.
\end{problem}

\begin{proof}
The proof is by contradiction. Assume the language $B$ is context free. Let $p$ be the pumping length given by the pumping lemma. Choose the string $s = 0^p1^p1^p0^p$. Clearly $s \in B$ and $|s| \geq p$. The pumping lemma states that $s$ can be pumped, but we show that it cannot be pumped.

\begin{enumerate}
\item Either $v$ or $y$ is non-empty. Without the loss of generality, we only discuss the case when v is non-empty. If v is non-empty, then it may contain only one type of alphabet or both 0’s and 1’s. In former case, the string $uv^2xy^2z \notin B$, because it cannot contain equal number of 0’s and 1’s. In latter case, the string $uv^2xy^2z \notin B$, because it is not a palindrome.
\item Both $v$ and $y$ are non-empty. There are three possibilities. First, both $v$ and $y$ contain the same type of alphabet from the same segment of either 0’s or 1’s. Second, $v$ and $y$ contain different type of alphabets from two neighboring segments of 0's and 1's. Third, both $v$ and $y$ contain 1's, but from two different segments of 1’s. In all three cases, the string $uv^2xy^2z \notin B$, because either it contains unequal number of 0's and 1's or the string is not a palindrome.
\end{enumerate}

One of these cases must occur, and both cases result in a contradiction. Therefore, the language $B$ is not context free.
\end{proof}

\end{document}
